---
title: "ED_Prepare_Datasets"
output: html_notebook
---
# Author: Vince Fasanello
# Date: June 2021
# Project: Fluctuating selection project, Evolutionary Dynamics Data Preparation


# File Description:-------------------------------------------------------------
#   
#   |-----------------------------------------------------------------------|
#   | This script, run in it's entirety, converts the raw counts data       |
#   | generated in step: 1_FastQtoCounts to as set of dataframes formatted  |
#   | for analysis in step: 3_Analysis                                      | 
#   |-----------------------------------------------------------------------|
# 
# Inputs-&-Outputs: -------------------
# 	Inputs:
# 		[1] A layout file specifying important aspects of the project design.
#         * LAYOUT FILE IS IDENTICAL TO LAYOUT FILE IN 1_FastQtoCounts DIRECTORY *
#         
# 		[2] A ".Rdata" type file containing a counts matrix named
# 		    "counts.expected" countaining counts mapping to expected barcodes for
#         each experiment based on the experimental design (Layout.csv).
#         * this file is created in step: 1_FastQtoCounts. *
#
# 		[3] A ".Rdata" type file containing a counts matrix named
# 		    "counts.unexpected" countaining counts mapping to unexpected barcodes for
#         each experiment based on the experimental design (Layout.csv).
#         * this file is created in step: 1_FastQtoCounts. *
# 			
# 	Outputs:
# 		[1] "swref.rdata" : A ".Rdata" type file containing data for single-well reference samples
#                          used  downstream to assess barcode contamination during evolution.
#
# 		[2] "dnablnk.rdata" : A ".Rdata" type file containing data for dna blank samples
#                           used downstream to assess barcode contamination during dna sample prep.
#
# 		[3] "pcrblnk.rdata" : A ".Rdata" type file containing data for dna blank samples
#                           used downstream to assess barcode contamination during pcr.
# ------------------------------------------------------------------------------ 		 

***
# Setup Script
Prepare the workspace set global options, load packages, set directories, etc..
```{r}
rm(list=ls()) # clear workspace
knitr::opts_chunk$set(tidy = TRUE) # set global knitr options.
options(scipen = 999) # turn off scientific notation
require(plyr, quietly = T) # load required packages
dir_in_1 <- paste0(getwd(),"/Counts_Data") # input: data
dir_in_m <- paste0(getwd(),"/Metadata") # input: metadata
dir_out_f <- paste0(getwd(),"/Formatted_Data") # output: dataframe formatted for analysis
```
<br/><br/>

Load and prepare the metadata file
```{r}
setwd("..")
setwd(dir_in_m)
lay <- read.csv("Layout.csv", header = T, stringsAsFactors = F)
```
<br/><br/>

Load and prepare the counts data
```{r}
setwd("..")
setwd(dir_in_1)
load(file = "Counts_Expected.Rdata") # expected counts
ec <- counts.expected; rm(counts.expected)
ec <- t(ec) # transpose to match metadata format: experiments are rows
ec <- ec[,1:(ncol(ec) - 1)]

load(file = "Counts_Unexpected.Rdata") # unexpected counts (barcode cross contamination)
uc <- counts.unexpected; rm(counts.unexpected)
uc <- t(uc) # transpose to match metadata format: experiments are rows
uc <- uc[,1:(ncol(uc) - 1)]
```
<br/><br/>

Fix A's and B's assignment for COPR timepointws 43 and 49.
```{r}
# plates COPR A and COPR B LABELS were switched for day 43 and day 49 data collection (relative to other timepoints). This block updates formatting to reflect this.
#time 43
tmpa <- ec[81,]
tmpb <- ec[90,]
ec[81,] <- tmpb; rownames(ec)[81] 
ec[90,] <- tmpa; rownames(ec)[90]

tmpa <- uc[22:24,]; rownames(tmpa) <- rownames(uc[25:27,])
tmpb <- uc[25:27,]; rownames(tmpb) <- rownames(uc[22:24,])
uc[22:24,] <- tmpb 
uc[25:27,] <- tmpa


#time 49
tmpa <- ec[22:24,]; rownames(tmpa) <- rownames(ec[25:27,])
tmpb <- ec[25:27,]; rownames(tmpb) <- rownames(ec[22:24,])
ec[22:24,] <- tmpb 
ec[25:27,] <- tmpa

tmpa <- uc[22:24,]; rownames(tmpa) <- rownames(uc[25:27,])
tmpb <- uc[25:27,]; rownames(tmpb) <- rownames(uc[22:24,])
uc[22:24,] <- tmpb 
uc[25:27,] <- tmpa
```
<br/><br/>

Combine metadata with counts data
```{r}
myd <- cbind(lay, ec)
myd$ppects <- rowSums(ec, na.rm = T) # primer pair expected counts  *BLANKS WILL BE ZERO HERE!!!!*
myd$ppccts <- rowSums(uc, na.rm = T) # primer pair cross-contam counts *THESE ONLY MAKE SENSE FOR SINGLE WELL CONTROLS!!!*
rm(lay, ec, uc)
```
<br/><br/>

Calculate primer pair summary statistics for the only 5 available samples.
```{r}
myd$cc <- (myd$ppccts / (myd$ppects + myd$ppccts)) 
myd$cc[myd$sample.type %in% c("plate", "dna_blank", "pcr_blank")] <- NA
```
<br/><br/>

Split out datasets of interest and save.
```{r}
setwd("..")
setwd(dir_out_f)

# read on cross contam
swref <- myd[myd$sample.type == "sw",] # sequence of wells containing only the reference strain run through the fitness assay, for cross contamination estimation. 
swref$ppcctsm <- swref$ppccts/110  # counts per contaminant
swref$ccm <- swref$cc/110 # cc rate per contaminant
save(swref, file = "swref.Rdata")

# controls...
dnablnk <- myd[myd$sample.type == "dna_blank",] # dna blank -- samples processed through full processing with DNA free water added instead of resuspended yeast
save(dnablnk, file = "dnablnk.Rdata")
pcrblnk <- myd[myd$sample.type == "pcr_blank",] # pcr blanks -- samples from every round of pcr -- included all components necessary for replication other than yeast DNA 
save(pcrblnk, file = "pcrblnk.Rdata")

rm(swref, dnablnk, pcrblnk)
# ------------------------------------------------
myd <-  myd[myd$sample.type == "plate",] # the data for processing
```
<br/><br/>